Our peculiar motion across the Universe

### 2019-06-25 paper/main.tex
new plots in main
new plot
edit

\documentclass[twocolumn]{aastex62}
\submitjournal{ApJL}
\title{Our peculiar motion across the Universe}
\shortauthors{Forero-Romero}

@@

>>>>

\documentclass[onecolumn]{aastex62}
\submitjournal{ApJL}
\title{Our peculiar motion across the Universe}
\shortauthors{Forero-Romero}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.4\textwidth]{cumulative_alignment_06.pdf}
\end{center}
\caption{Cumulative probability for the dot product between the unit
  vector joining the two dominan halos in the pair and the peculiar
  velocity of the less massive halo.
  Continous line: results for all pairs; dashed line: pairs where the
  less massive halo moves with a pecular velocity larger than
  $v_p=627\pm22$ km s$^{-1}$.}
\label{fig:alignment}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{ratio_pair_total_ind_total.pdf}
\end{center}
\caption{Ratio}
\label{fig:ratio_total}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{ratio_pair_high_ind_total.pdf}
\end{center}
\caption{Ratio}
\label{fig:ratio_fast}
\end{figure*}
